The dynamics of risk perception in a Mediterranean agroecosystem

### 2020-02-13 manuscript/manuscript.Rmd
refine prior update plot

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
library(raster)
library(ncdf4)
library(tidyverse)
```

@@

```{r, fig.width = 5, fig.height = 3, fig.cap = "Change in perceived drought risks in an older (50) and younger (15) agent before and after a 25-year dry period."}
prior2 <- function(a, b) {
  domain <- seq(0,1,0.005)
  val <- dbeta(domain, a, b)
  tibble('x' = domain, 'y' = val)
}

tibble(alpha = c(15 * 0.2, 50 * 0.2, 15 * 0.2 + 25 * 0.4, 50 * 0.2 + 25 * 0.4),
       beta = c(15 * 0.8, 50 * 0.8, 15 * 0.8 + 25 * 0.6, 50 * 0.8 + 25 * 0.6),
       time = c('before', 'before', 'after', 'after'),
       age = c('young', 'old', 'young', 'old')) %>%
  mutate(belief = map2(alpha, beta, ~prior2(.x, .y))) %>%
  unnest(cols = c(belief)) %>%
  ggplot(aes(x, y)) +
  geom_line(aes(group = time, color = time), size = 1.2, alpha = .8) +
  #scale_color_viridis_d(guide = 'legend') +
  facet_wrap(~age) +
  labs(x = expression('Drought probability (' * theta * ')'), y = 'Density') +
  theme_classic()
```

@@

```{r, fig.height = 4, fig.width = 6}
test1 <- tibble(time = 1:75,
       risk = c(rep(0.2, 25), rep(0.4, 25), rep(0.2, 25)))

ggplot(sim1, aes(time, risk)) +
  geom_line(data = test1) +
  geom_point(alpha = .1) +
  geom_hline(yintercept = indiff$risk, color = 'red', linetype = 2) +
 # geom_smooth(color = 'darkorange') +
  theme_classic()
```

```{r}
sim1 %>%
  group_by(time, crop) %>%
  tally() %>%
ggplot(aes(time, n, fill = crop)) +
  geom_bar(width = 1, stat = 'identity', position = 'fill') +
  scale_fill_manual(values = c('darkgoldenrod', 'lightgoldenrod')) +
  theme_classic()
```

```{r}
library(furrr)
plan(multisession)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
library(raster)
library(ncdf4)
library(tidyverse)
library(patchwork)
```

@@

```{r, fig.width = 6, fig.height = 3, fig.cap = "Change in perceived drought risks in an older (50) and younger (15) agent before and after a 25-year dry period."}
prior2 <- function(a, b) {
  domain <- seq(0,1,0.005)
  val <- dbeta(domain, a, b)
  tibble('x' = domain, 'y' = val)
}

tibble(alpha = c(15 * 0.2, 50 * 0.2, 15 * 0.2 + 25 * 0.4, 50 * 0.2 + 25 * 0.4),
       beta = c(15 * 0.8, 50 * 0.8, 15 * 0.8 + 25 * 0.6, 50 * 0.8 + 25 * 0.6),
       time = factor(c('prior', 'prior', 'posterior', 'posterior'), levels = c('prior', 'posterior')),
       age = factor(c('15-year-old agent', '50-year-old agent', '15-year-old agent', '50-year-old agent'), levels = c('15-year-old agent', '50-year-old agent'))) %>%
  mutate(belief = map2(alpha, beta, ~prior2(.x, .y))) %>%
  unnest(cols = c(belief)) %>%
  ggplot(aes(x, y)) +
  geom_line(aes(group = time, color = time), size = 1.2, alpha = .8) +
scale_color_manual(values = c('purple', 'orange'), name = '') +
    facet_wrap(~age, strip.position = 'bottom') +
    theme_classic() +
  theme(strip.background = element_blank(),
        legend.position = c(.43, .5),
        strip.placement = "outside") +
  labs(x = expression('Drought probability (' * theta * ')'), y = 'Density')
```

@@

```{r, fig.height = 8, fig.width = 7}

a <- ggplot(sim1) +
  geom_rect(aes(xmin = 25, xmax = 50, ymin = -Inf, ymax = Inf), fill = NA, color = 'black', alpha = .002) +
  geom_point(aes(time, risk), alpha = .1) +
  geom_hline(yintercept = indiff$risk, color = 'red') +
  theme_classic()

b <- sim1 %>%
  group_by(time, crop) %>%
  tally() %>%
ggplot(aes(time, n, fill = crop)) +
  geom_bar(width = 1, stat = 'identity', position = 'fill') +
  scale_fill_manual(values = c('darkgoldenrod', 'lightgoldenrod')) +
  theme_classic()

a / b
```

```{reval=FALSE}
library(furrr)
plan(multisession)
